module2graphsandPCA

### 2022-03-15 module2graphsandPCA.Rmd
more formatiing changes in rmd
knitting to pdf

---
title: "module2graphsandPCA"
output:
  html_document:
    fig_width: 10
    fig_height: 7
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@

ecopolscalescores
```

>>>>

---
title: "module2graphsandPCA"
output:
  pdf_document: 
    toc: true
    number_sections: true
    toc_depth: 2
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    df_print: paged
  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@
